---
title: "MechaCarChallenge"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Dependency
```{r}
library(dplyr)
library(tidyverse)
```
### Read CSV file
```{r}
mpg <-read_csv("C:/Users/tearo/Desktop/MechaCar_mpg.csv")
'show_col_types = FALSE'
```
### Preview MechaCar_mpg
```{r}
head(mpg)
```
### Perform linear regression using the lm() function
```{r}
lm(mpg ~ mpg + AWD + ground_clearance + spoiler_angle+ vehicle_weight + vehicle_length,data=mpg) #generate multiple linear regression model
```

### Using the summary() function
```{r}
summary(lm(formula = mpg ~ mpg + AWD + ground_clearance + spoiler_angle + 
    vehicle_weight + vehicle_length, data = mpg)) #generate summary statistics
```



### plot
```{r}
par(mfrow = c(2, 2)) 
plot(lm(formula = mpg ~ mpg + AWD + ground_clearance + spoiler_angle + 
    vehicle_weight + vehicle_length, data = mpg))
```

### Read CSV file
```{r}
coil <-read_csv("C:/Users/tearo/Desktop/Suspension_Coil.csv")

```
### Preview Suspension_Coil
```{r}
head(coil)
```
### Calculate the average
```{r}
mean_PSI <- summarize(coil, mean(PSI))
paste("The average PSI is", mean_PSI)

```
### Calculate the MEDIAN
```{r}
median_PSI <- summarize(coil, median(PSI))
paste("The median PSI is", median_PSI)

```
### Calculate the Variance
```{r}
var_PSI <- summarize(coil, var(PSI))
paste("The variance of PSI is", var_PSI)

```
### Calculate the SD
```{r}
sd_PSI <- summarize(coil, sd(PSI))
paste("The standard deviation of PSI is", sd_PSI)

```
### total_summary 
```{r}
total_summary <-  summarize(coil, mean_PSI, median_PSI, var_PSI, sd_PSI)

```
### lot_summary
```{r}
lot_summary <- coil %>% group_by(Manufacturing_Lot) %>%   summarize(Mean=mean(PSI),Median=median(PSI),Variance=var(PSI),SD=sd(PSI), .groups='keep')
```
### T-test
```{r}
t.test(coil$PSI,mu=1500)

```
### Use t.test() function 3 more times with subset() to determine if PSI for each manufacturing lot is statistically different from the pop. mean of 1,500 PSI
```{r}
lot1 <- subset(coil, Manufacturing_Lot=="Lot1")
lot2 <- subset(coil, Manufacturing_Lot=="Lot2")
lot3 <- subset(coil, Manufacturing_Lot=="Lot3")
t.test(lot1$PSI,mu=1500)
t.test(lot2$PSI,mu=1500)
t.test(lot3$PSI,mu=1500)

```
